### 2021-03-24 notes/notes.tex
Changed pars a bit for big sim in office

\section{Simulation results}
\subsection{Effects of observation noise on inference}
Observation noise refers to the noise on the position of the hand. The generating process is a Gaussian with $\sigma = 0.1$, which is determined in ./code/adaptation/pars.py. However, the agent has a belief on this value, which is fixed for the agent. This value (obs_sd, which can be passed on instanciation) can be used in lieu of an explicit $\Delta t$ parameter which controls the size of the time step

>>>>

\section{Simulation results}
\subsection{Effects of observation noise on inference}
Observation noise refers to the noise on the position of the hand. The generating process is a Gaussian with $\sigma = 0.1$, which is determined in ./code/adaptation/pars.py. However, the agent has a belief on this value, which is fixed for the agent. This value (obs\_sd, which can be passed on instanciation) can be used in lieu of an explicit $\Delta t$ parameter which controls the size of the time step

\subsection{Parameter values to look into}
By visual inspection of the results of simulations, these are the parameter values that seem promising:

\begin{tabularx}{\textwidth}{
  >{\hsize=.2\hsize\linewidth=\hsize}X|
  >{\hsize=.1\hsize\linewidth=\hsize}X|
  >{\hsize=.1\hsize\linewidth=\hsize}X|
  l}
% {l|{\hsize=.4\hsize}X|{\hsize=0.3\hsize}X|{\hsize=0.3\hsize}X}
Agent & Obs noise & Cue noise & Notes \\ \hline \hline
LR    & 1.2       & 0.04      & Slow fake-context inference. Maybe the priors coming from the previous stage are messing things up. \\ \hline
1 & 1 & 1 & 1
\end{tabularx}
